---
title: "PU5558-assessment1"
author: "52104039"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load necessary packages

It is good practice to load the packages to be used before commencing analysis and coding.
```{r load-packages}
library(tidyverse)    # for general data science
library(tidymodels)   # for machine learning
library(readr)
```  

## Load chosen dataset

The dataset chosen for this project is the Knee Replacement Procedure dataset.

```{r read-data}
knee_data <- "input/Knee Replacement CCG 2021.csv" %>% read.csv()

glimpse(knee_data)
summary(knee_data)
```

## Dataset description

the dataset to be used contains Provisional Patient Reported Outcome Measures(PROMS)before and after a knee replacement surgery which took place in England, from April 2020 to March 2021

## Suitable machine learning algorithm for three questions:

1. Before the operation, can we estimate the post-operative EQ5D index for a patient?


2. Before the operation, can we predict how much pain a patient will have after the operation?


3. Before the operation, can we calculate how many patients have had previous surgery? 




## Model building to answer chosen question

1.	Data splitting

```{r}

```

2.	Selection and preprocessing of predictors

```{r}

```

3.	Model specification and training

```{r}

```

4.	Model evaluation

```{r}

```

## Limitations of machine learning model

